STM single case

### 2019-04-04 Messy Code/stm single case.Rmd

---
title: "Pillar 2 - (STM) Topic Modeling"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache.path = "Cache/Pillar 2/",
                      eval = FALSE)
```

@@

##Functions for internal faceting
```{r function reorder_within & co., echo = FALSE, eval = TRUE}

# Function for ordering within facet:
# https://github.com/dgrtwo/drlib/blob/master/R/reorder_within.R

reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
  new_x <- paste(x, within, sep = sep)
  stats::reorder(new_x, by, FUN = fun)
}

scale_x_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
}

scale_y_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_y_discrete(labels = function(x) gsub(reg, "", x), ...)
}
```

##Loading data
We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
`d_course`, `d_transcript`, and a list `d_text` with the textual data for catalogues and manuals (for $overview, $description, $manuals we have (`Course ID`, `year`, `word_original`, `word`) ).

For `d_text` we keep only the most recent year.
```{r import data, eval = TRUE}
#load
#load("output/data_pillar_2.RDATA")
load("Output/d_text.RDATA")

# keep most recent year
#d_text <- d_text %>% map(function(tb, y) tb %>% filter(year == max(year)))
```
###As corpus
```{r}

```
# TF-IDF
We will perform an initial (visual) exploratory analysis of our textual data using TF- IDF.

## Functions for Generating Barplots and Word Clouds
The function `compute_tf_idf` computes the inverse term document frequency, we apply `compute_tf_idf` on descriptions, overviews and manuals. 
```{r compute_tf_idf, cache = TRUE}
#
##Function
compute_tf_idf <- function(data){

  data %>%
    count(
      `Course ID`,
      word
      ) %>%
    bind_tf_idf(
      term = word, 
      document = `Course ID`,
      n = n
      )
}

#
##Application
tf_idf <- map(d_text, .f = compute_tf_idf)

#
##Clean workspace
rm(compute_tf_idf)
```

The function `plot_tf_idf` plots a bar-graph of the most important words for each level of granularity and  their corresponding word clouds. 
```{r plot_tf_idf}
plot_tf_idf <- function(data, n_col = 5, id_plot = NULL){

  #
  # Barplot
  g <- data %>%
    ggplot(
      aes(
        x = reorder_within(word, tf_idf, facet), 
        y = tf_idf
        )
      ) +
    geom_col(
      show.legend = FALSE
      ) +
    labs(
      x = NULL,
      y = "tf-idf"
      ) +
    scale_x_reordered() +
    facet_wrap(
      facets = ~ facet, 
      scales = "free",
      ncol = n_col
      ) +
    coord_flip()

  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)

  #
  # Word Cloud
  g <- data %>%
    group_by(
      facet
      ) %>%
    mutate(
      freq = tf_idf / sum(tf_idf)
      ) %>% # normalization within facet
    ggplot(
      aes(
        size = freq ^ 0.7, 
        label = word, 
        color = freq ^ 0.7
        )
      ) +
    geom_text_wordcloud_area(
      area_corr_power = 1,
      eccentricity    = 1,
      rm_outside      = T
      ) +
    scale_radius(
      range = c(2, 10),
      limits = c(0, NA)
      ) +
    scale_color_gradient(
      low = "red", 
      high = "blue"
      ) +
    facet_wrap(
      facet = ~ facet,
      ncol = n_col
      ) + 
    theme(
      strip.text.x     = element_text(),
      panel.background = element_rect(fill = "white"),
      plot.title       = element_text(hjust = 0.5)
    )

  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)

}
```

## Course Level
The function `prepare_tf_idf_course` selects 25 random courses, the top ten words with highest tf_idf, and finally renames a facet to 'Course ID').
We apply the function to `id_plot` and pipe it to produce graphs.
```{r tf-idf course, cache = TRUE}
prepare_tf_idf_course <- function(data){

  data %>%

    # Selection 25 courses randomly
    filter(
      `Course ID` %in% sample(
        x = unique(.$`Course ID`),
        size = 25, 
        replace = FALSE
        )
      ) %>%

    # Select top 10 words per course 
    group_by(
      `Course ID`
      ) %>%
    filter(
      n >= 2
      ) %>%
    top_n(
      n = 10,
      wt = tf_idf
      ) %>%
    ungroup %>%

    # Prepare data for function `plot_tf_idf()`
    rename(
      facet = `Course ID`
      )

set.seed(123)
tf_idf$overview %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(id_plot = "Course_overview")

set.seed(123)
tf_idf$manual %>%
  prepare_tf_idf_course %>%
  plot_tf_idf(id_plot = "Course_manual")

rm(prepare_tf_idf_course)
```

## Cluster Level
```{r tf-idf cluster, cache = TRUE}
prepare_tf_idf_cluster <- function(data){

  data %>%

    # Include the variable Cluster
    left_join(
      select(d_course, `Course ID`, Cluster),
      by = "Course ID"
      ) %>%
    filter(
      !is.na(Cluster)
      ) %>%

    # Select top 10 words per cluster
    group_by(
      Cluster, 
      word
      ) %>%
    summarise(
      tf_idf = sum(tf_idf),
      n = sum(n)
      ) %>%
    filter(
      n >= 10
      ) %>%
    top_n(
      n = 10, 
      wt = tf_idf
      ) %>%
    ungroup %>%

    # Prepare data for function `plot_tf_idf()`
    rename(
      facet = Cluster
      )

tf_idf$overview %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(id_plot = "Cluster_overview")

tf_idf$manual %>%
  prepare_tf_idf_cluster %>%
  plot_tf_idf(id_plot = "Cluster_manual")

rm(prepare_tf_idf_cluster)
```

## Concentration Level
```{r tf-idf concentration, cache = TRUE}
prepare_tf_idf_concentration <- function(data){

  data %>%

    # Include the variable Concentration
    left_join(
      select(d_course, `Course ID`, Concentration, `Concentration (additional)`),
      by = "Course ID"
      ) %>%
    filter(
      !is.na(Concentration)
      ) %>%
    gather(
      key = X,
      value = Concentration,
      Concentration, `Concentration (additional)`,
      na.rm = TRUE
      ) %>%

    # Select top 10 words per cluster
    group_by(
      Concentration, 
      word
      ) %>%
    summarise(
      tf_idf = sum(tf_idf),
      n = sum(n)
      ) %>%
    filter(
      n >= 10
      ) %>%
    top_n(
      n = 10,
      wt = tf_idf
      ) %>%
    ungroup %>%

    # Prepare data for function `plot_tf_idf()`
    rename(
      facet = Concentration
      )

tf_idf$overview %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(id_plot = "Concentration_overview")

tf_idf$manual %>%
  prepare_tf_idf_concentration %>%
  plot_tf_idf(id_plot = "Concentration_manual")

rm(prepare_tf_idf_concentration, plot_tf_idf)
```

@@

    lbound             = bound + lfact,
    iterations         = map_dbl(Model,       
                                 function(model) length(model$convergence$bound))
    ) 
```
###Saving Results
```{r save}
#saving
my_models <-  list(use = stm_model, eval = stm_eval_model)
save(my_models , file="STM_models.RDATA")
```

```{r clean workspace}
#clean workspace
rm(# Generating functions:
  my_stm, my_stm_eval,
  #Extraction Functions
  extract_dtm, extract_corpus, extract_documents, extract_vocab, extract_data,
  extract_held_doc, extract_held_vocab, extract_helout_missing, 
  my_model, my_tidy_gamma,
  get_top_terms_topic, 
  get_top_topics_course,
  get_kw
  )
```

##Finding Number of Topics
We want to estimate the number of topics that exist in the data, to select a model for them.

###Using search K
`stm::searchK` helps in the search.
The function `findK` is used to vectorise searchK so we can apply it to the different elements of our corpus list (overview, manuals, description) in one go.
```{r findK}
#findK function 
findK <- function(dtm, k_topics){
  searchK(dtm$documents, dtm$vocab, K = k_topics, init.type = "Spectral")
}
```

We train models for 74 different numbers of topics (14-200 by 2).
Time estimate: for seq(from = 50, to = 100, by = 10) #18 models trained took 4:31-3:09 = (1 hour and 22 min)
```{r finding K}
#select number of topics
k_topics = seq(from = 4, to = 150, by = 2)

#Run findK
findingK <- stm_corpus %>%
  map(findK, k_topics)
```
We inspect the findings:
```{r plot evaluation- package}
findK_plots <- map(findingK, plot) #see how to show.
```

```{r save findK}
#save files
save(findingK, file= "STM_estimate_k.RDATA")

#clean
rm(findK, k_topics)
```
###From stm_eval
```{r manual eval plots}
#Function
plot_eval <- function(origin){
stm_eval_model %>%
  filter(Origin == origin) %>%
  transmute(n_topic,
            `Lower bound` = lbound,
             Residuals    = map_dbl(residual, "dispersion"),
            `Semantic coherence` = map_dbl(semantic_coherence, mean),
            `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")) %>%
  gather(Metric, Value, -n_topic) %>%
  ggplot(aes(n_topic, Value, color = Metric)) +
  geom_line(size = 1.5, alpha = 0.7, show.legend = FALSE) +
  geom_point()+
  facet_wrap(~Metric, scales = "free_y") +
  labs(x = "Number of Topics)",
       y = NULL,
       title = "Model diagnostics by number of topics")
}

#Create plots
plot_eval("manuals")
plot_eval("overview")
```
#Vizualization
```{r extract topic model}
select_topic_model <- function(origin, n_topic){
  model <- stm_model %>% 
    filter(Origin == origin & n_topic == n_topic) %>%
    pull(Model)

  model <- model[[1]]
  return(model)
}

test <- select_topic_model("catalogues", 10)

plot.STM(test, "perspectives", topics = c(1,5))
```
#New Documents
##Align vocabulary
```{r align vocab}
#back up current code
d_text1 <- d_text

#single case: Fasos topics
fasos_docs <- d_text$catalogues %>%
  filter(department == "European_studies") %>%
  select(-department)

fasos_cast <- my_cast_dtm(fasos_docs)

```
##Fit new docs
```{r}
# fitting:
out <- asSTMCorpus(fasos_cast)
newdocs <- alignCorpus(new=out, old.vocab = model$vocab)
fasos_theta <- fitNewDocuments(model = model, documents=newdocs$documents) #returns a course by topic matrix

my_names <- names(newdocs$documents)

fasos_theta$theta #nice kind of makes sense
plot.STM(model, type ="summary")

rownames(fasos_theta$theta) <- my_names

new_courses_theta <- fasos_theta$theta

set_names(fasos_theta$theta, old = colnames(fasos_theta$theta), new = paste0("Topic", 1:10))

new_courses_theta %>%  mutate(Topic = paste("Topic_", rownames))
```
#Experiment
```{r experoment}
estimateEffect(formula = 1:5 ~department, meta = test$meta)

>>>>

---
title: "STM single case"
author: "DARS"
date: "4/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

##Loading data
We load the environment `Output/d_text.RDATA`. It contains the data sets:
`d_course`, `d_transcript`, and a list `d_text` with the textual data for catalogues and manuals (for $overview, $description, $manuals we have (`Course ID`, `year`, `word_original`, `word`) ).

For `d_text` we keep only the most recent year.
```{r import data, eval = TRUE}
#load
load("Output/d_text.RDATA")
```

@@

    lbound             = bound + lfact,
    iterations         = map_dbl(Model,       
                                 function(model) length(model$convergence$bound))
    ) 
```
